Supplementary Materials

### 2023-06-22 manuscript/manuscript.tex
ms updates

The continual influx of new mutations into populations is the ultimate source
of all adaptations, but the vast majority of mutations either do not affect
fitness or are deleterious. Negative selection works to eliminate such
deleterious mutations from the population, which is essential to maintaining
the integrity of information in the genome needed to maintain a lineage.
Mutations under negative selection are kept at low frequencies (Haldane?),
contributing to human traits (XXX) and diseases. As with most selection in the
genome, this process perturbs the allele frequencies of neighboring linked
variation. This reduces genetic variability around conserved segments and
creates large-scale spatial ``linked selection signal" in genetic diversity.
Mutation and negative selection's contribution to this signal is mediated by
the deleterious mutation rate, the strength of selection in conserved segments,
and the spatial distribution of recombination rates and conserved segments.
Since genome-wide recombination maps and putatively conserved segments are
available for many species, researchers have combined these with population
genetic theory to estimate the mutation rate and selection coefficients of
deleterious mutations, as well as the overall reduction in genetic variability
due to the negative selection process.

Classic Background Selection (BGS) theory is the predominant model for the
reduction in linked neutral diversity used by statistical approaches to
quantify the impacts of negative selection. However, this model makes some
assumptions for mathematical tractability that could distort inferences about
the negative selection process. First, since fixation probabilities ultimately
depend on the product of the deleterious selection coefficient (s) and
population size (N), the efficacy of negative selection should depend on
demography. Unfortunately, accommodating demography into theoretic negative
selection models remains an open, difficult problem (XXX). Second, building off
classic models of mutation-selection balance (Crow 1970, Kimura and Maruyama
196), the Background Selection (XXX) model assumes that new mutations are
sufficiently deleterious that they are invariably driven to loss. Under this
assumption, the effect of selection is well-approximated by simply rescaling
the neutral coalescent by a reduction factor known as B (XXX). However, this is
only appropriate in a limited domain of parameters relevant to the negative
selection process (XXX). Because the BGS model cannot accommodate the
possibility of fixation for mutations with $Ns \ll 1$, diversity is incorrectly
predicted to fall to zero as the strength of selection diminishes. This weak
selection problem is related to the wider problem of modeling the substitution
rate of deleterious mutation (i.e. the “ratchet” rate). Third, the BGS model
assumes segments under purifying selection are sufficiently far apart that
there is no selective interference between them. This is a matter of degree,
since under sufficiently high mutation rates or with little recombination,
selective interference can occur with a segment.

@@

However, unlike non-heritable variation in offspring number, the heritable
variation is autocorrelated across generations. At the individual level
Robertson considered, this is because offspring from large families tend to
beget many descendents themselves (and likewise with small families). The same
autocorrelation occurs at the genomic level, as the perturbations to a neutral
allele's trajectory from its particular fitness background tend to occur in the
same direction across generations as long as the linkage exists and the
selective environment is constant. The additional heritable variation in
offspring number is the additive fitness variation $V_A$, which is inflated by
a factor $Q_t^2$ due to the build up of autocorrelation to generation $t$. We
let $Q^2 = Q_t^2$ as $t \to \infty$. Intuitively, the product $V_A Q^2$
represents the expected total variance in reproductive success a neutral
mutation experiences over its lifetime in a system with draft. Incorporating
the impact of time-invariant autocorrelation created by draft as a rescaled
rate of drift is analogous to using the Green--Kubo relation to find the
transport coefficient in molecular dynamics with velocity autocorrelation
\parencite{Green1954-kl,Kubo1957-va}.

@@

Equation \eqref{eq:main_Ne} is general, since different modes of selection and
linkage can be accommodated by different expressions for the inflation factor
$Q^2$. When fitness variation has a multiplicative polygenic basis, as it does
for genome-wide negative selection processes, the draft asymptotic effective
population size experienced by an arbitrary neutral site under the influence of
all linked regions is,

@@

where the factor of one-half comes from ignoring weak associations from
unlinked regions and chromosomes (see XXX). In our genome-wide model, we
consider the summation in Equation \eqref{eq:polygenic_Ne} over non-overlapping
segments $i \in \{1, 2, \ldots, n\}$ each undergoing selection such that
segment $i$ contributes additive fitness variance $V_{A,i}$ to the total
additive genetic fitness variance. Under equilibrium levels of fitness
variation, the autocorrelation function for a neutral allele associated with
segment $i$ is the time-invariant function $C(t) = [(1-r_i)(1-\kappa_i)]^t$,
where $r_i$ is the recombination fraction to the segment and $\kappa_i$ is the
rate that the associated fitness variance decays due to selective dynamics.
Then, the cumulative autocorrelation is,

@@

The remaining pieces are expressions for the equilibrium additive fitness
variance $V_A$ and the decay rate in associated fitness $1-\kappa$. At this
point, we diverge from Santiago and Caballero (\citeyear{Santiago1998-bs},
\citeyear{Santiago2016-mu}) to note that the additive fitness variation is the
sum of additive \emph{genic} fitness variance $V_a$ (i.e. due to allele
frequencies) and the total linkage disequilibria $\delta_{LD}$ between selected
sites, $V_A = V_a + \delta_{LD}$. Considering only the genic variation, at
equilibrium $\Delta V_{a,i} = 0$; thus, the loss in genic fitness each
generation due to selective dynamics $-\kappa V_{A,i}$ must be equal to the
increase in fitness variation to new mutations $V_m$ each generation and
changes in the LD term \parencite{Bulmer1971-ae}. Note that the loss in genic
fitness due to drift is not time-invariant due to the build up of
autocorrelation, and considered elsewhere in the derivation (see Supplementary
Materials Equation \ref{eq:vardecay}). Then, $\kappa_i =
\nicefrac{V_{m,i}}{V_{a,i}}$ (see Supplementary Materials Equation \ref{eq:Z}).

@@

When selection is weak, however, the additive fitness variance under the
classic BGS model is no longer accurate. \parencite{Santiago2016-mu} suggested
that this is due to the loss of fitness variation that occurs when a
segregating site fixes and its heterozygosity becomes zero. If we let $R$
represent the rate of the ratchet of deleterious mutations in fixations per
generation, each fixation removes the equivalent amount of equilibrium
variation put in by mutation. Thus, the steady-state genic variance under
mutation and negative selection is (omitting the segment index $i$ for
clarity),

@@

where the condition $V_a \ge 0$ is met when the probability of fixation is less
than or equal to the neutral fixation probability of $\nicefrac{1}{2N}$, which
is held when considering deleterious mutations. This equation connects the
equilibrium additive genic fitness variance to the flux of new variation in due
to new deleterious mutations and the flux out due to their substitution and the
decline in mean population fitness. When $R=0$, the selection is so strong it
cannot fix, and the equilibrium fitness variation is due entirely to young rare
mutations before their extinction $V_a = V_a^{BGS} = Us$. Santiago and
Caballero demonstrate Equation \eqref{eq:Va} through Fisher's Fundamental
Theorem of Natural Selection, but we find an alternative proof
(\cite{Higgs1995-xc}; see Supplementary Materials Section
\ref{supp:weak-strong}). We find that the steady-state additive genic variance
in Equation \eqref{eq:Va} also results from diffusion models with a flux of
mutations into discrete sites (\cite{Kimura1969-jw}; see Supplementary
Materials Section \ref{supp:kimura}). Our results differ from
\parencite{Santiago2016-mu}, since we find from simulations their expression
models the additive \emph{genic} fitness variation, not additive genetic
fitness variation (see Section XXX). This is because Equation \eqref{eq:Va}
does not capture the expected build-up of negative linkage disequilibria when
selection is only mildly deleterious.

While using Equation \eqref{eq:Va} in Equation \eqref{eq:main_Ne} leads to a
prediction for the draft-effective population size $N_d$, closed-form
expressions for the rate of the ratchet $R$ have generally been hard to find
\parencite{Haigh1978-gt,Higgs1995-xc,Gessler1995-hz}. The key insight of
\textcite{Santiago2016-mu} is that the ratchet rate under draft is determined
by the probability of fixation $p_f(N_d, s)$
\parencite{Kimura1962-su,Malecot1948-zv} with the draft-rescaled effective
population size, e.g. $R = N U p_f(N_d, s)$. Given this equation for the
ratchet and Equation \eqref{eq:polygenic_Ne} for $N_d$ under draft, we have a
system of two non-linear equations that can be solved numerically for $N_d$ and
$R$ for each segment,

@@

Given that Santiago and Caballero's (\citeyear{Santiago2016-mu}) model is a
haploid-model for a single region under equilibrium negative selection, we
first sought to confirm it could accurately predict the reduction in realistic
forward-time simulations of diploid populations with recombination. Using SLiM
\parencite{Haller2019-vu,Haller2023-uk} we simulated a region of $10^5$
basepairs under varying levels of mutation and selection. We find a close
correspondence between the observed and predicted reduction in effective
population size $B=\nicefrac{N_d}{N}$ over all selection and mutation
parameters including weak selection (Figure \ref{fig:figure-1}A), in contrast
to classic BGS theory. Furthermore, to investigate whether this accuracy was
caused by the model capturing the equilibrium fitness variance and ratchet
rate, we also measured these throughout the simulation. Again, we find the
diploid SC16 theory accurately predicts both the ratchet rate (Figure
1\ref{fig:figure-1}B) and the genic fitness variance (Figure
1\ref{fig:figure-1}C).

Additionally, these figures provide further intuition for the underlying
negative selection process. When selection is strong the ratchet rate is zero,
as there is no probability that strongly deleterious can fix. However, around
$2N_e s \approx 1$, the ratchet begins clicking as $p_F > 0$. Ultimately, the
ratchet rate reaches the neutral mutation rate, as $V_a = 0$ and $N_d = N$
(e.g. no draft). Likewise, the additive genic fitness variance matches the
level predicted by BGS ($Us$), but begins to diverge when the ratchet begins
clicking. This occurs when the level of variation diverges from the
deterministic mutation-selection equilibrium $V_a = Us$ due to the stochastic
clicking of the ratchet at rate $R$.

@@

Given the accuracy of the SC16 model in predicting the reduction in effective
population size and ratchet rate when equilibrium negative selection processes
were acting in single segment, we extended their model so that it could be
applied to whole-genome data. Our method, implemented in the software
\texttt{bgspy}, calculates the equilibrium additive genic fitness variance
$V_a$ and ratchet rate $R$ for each specified segment in the genome for a range
of mutation rates and selection coefficients and a fixed genome-wide
drift-effective population size $N$ (see Methods XXX). Genomic regions
putatively under negative selection (e.g. coding sequences or UTRs) and the
recombination rate map are specified as arguments so that the predicted values
accurately reflect local genomic details. Note that each equation is solved
independently, since here we assume no selective interference between segments.
We refer to the prediction reductions along the genome from our approach as B'
maps (analogous to B maps from \cite{McVicker2009-ax}).

To assess our B' maps, we simulated negative selection for fixed mutation rates
and selection coefficient on human chromosome 10 using realistic recombination
and conserved feature maps. Averaging over $n=100$ simulation replicates, we
estimated the simulation expected reduction map and compared this to the
predicted B and B' maps for the same parameters. We find that our B' maps and
the classic BGS theory B maps closely match simulations when selection is
strong (top row of Figure \ref{fig:figure-1}E). This provides the first
realistic forward-time simulation confirmation of classic background selection
theory. However, we find slight discrepancies in regions with low recombination
(Figure \ref{fig:figure-1}E). Second, we find our theory is vastly more
accurate than the classic B maps when selection is very weak ($2N_e s \ll 1$;
bottom row of Figure \ref{fig:figure-1}E), which is expected since BGS theory
does not work in this domain. Across all mutation and selection parameters
simulated, the relative error of the classic B maps is 14.6\% whereas the
relative error in the new B' maps is 5\%. Additionally, we find that the mean
squared error between simulations and B' maps is close to the theoretic lower
bound set by the coalescence variance \parencite[see Methods
XXX]{Tajima1983-gu}.

Nearly all of the error between the new B' maps and chromosome-wide simulations
occurs around the drift-barrier domain of $2Ns \approx 1$ (Figure
\ref{fig:figure-1}D). The higher error in this domain occurs across all
mutation rates. First, we hypothesized that the reason this occurred was the
when we numerically solve Equations \eqref{eq:main_eqns} for each segment, this
does does not consider the reduction due to selection at other linked segments.
In particular, we use $N=1000$ corresponding to the number of diploids in the
simulations rather than $B'(x) N$ at position $x$. To test this, we implemented
a locally-rescaled version of the B' maps, which numerically solves Equations
\eqref{eq:main_eqns} for each segment at position $x$ taking into account the
reduction experienced due to selection at other segments by setting $B'(x)N$ as
the population size (see Method XXX). We find the locally-rescaled B' maps
reduce the relative error from 5\% to 0.4\% and mean squared error (Figure
\ref{fig:figure-1}D, dashed colored lines), but does not entirely eliminate the
error in the $2Ns \approx 1$ domain.

@@

\subsection*{Annotation Model Comparison}

@@

>>>>

The continual influx of new mutations into populations is the ultimate source
of all adaptations, but the vast majority of mutations either do not affect
fitness or are deleterious. Negative selection works to eliminate such
deleterious mutations from the population, which is essential to maintaining
the integrity of information in the genome needed to maintain a lineage.
Mutations under negative selection are kept at low frequencies (Haldane?),
contributing to human traits (XXX) and diseases. As with most selection in the
genome, this process perturbs the allele frequencies of neighboring linked
variation. This reduces genetic variability around conserved segments and
creates a large-scale spatial ``linked selection signal" in diversity alone the
genome. Mutation and negative selection's contribution to this signal is
mediated by the deleterious mutation rate, the strength of selection in
conserved segments, and the spatial distribution of recombination rates and
conserved segments. Since genome-wide recombination maps and putatively
conserved segments are available for many species, researchers have combined
these with population genetic theory to estimate the mutation rate and
selection coefficients of deleterious mutations, as well as the overall
reduction in genetic variability due to the negative selection process.

Classic Background Selection (BGS) theory is the predominant theoretic model to
predict the reduction in linked neutral diversity, and is used by statistical
approaches that quantify the aspects of the negative selection. However, the
BGS model makes some assumptions for mathematical tractability that could
distort inferences about the negative selection process. First, since fixation
probabilities ultimately depend on the product of the deleterious selection
coefficient (s) and population size (N), the efficacy of negative selection
should depend on demography. Unfortunately, accommodating demography into
theoretic negative selection models remains an open, difficult problem (XXX).
Second, building off classic models of mutation-selection balance (Crow 1970,
Kimura and Maruyama 196), the Background Selection (XXX) model assumes that new
mutations are sufficiently deleterious that they are invariably driven to loss.
Under this assumption, the effect of selection is well-approximated by simply
rescaling the neutral coalescent by a reduction factor known as B (XXX).
However, this is only appropriate in a limited domain of parameters relevant to
the negative selection process (XXX). Because the BGS model cannot accommodate
the possibility of fixation for mutations with $Ns \ll 1$, diversity is
incorrectly predicted to fall to zero as the strength of selection diminishes.
This weak selection problem is related to the wider problem of modeling the
substitution rate of deleterious mutation (i.e. the “ratchet” rate). Third, the
BGS model assumes segments under purifying selection are sufficiently far apart
that there is no selective interference between them. This is a matter of
degree, since under sufficiently high mutation rates or with little
recombination, selective interference can occur with a segment.

@@

However, unlike non-heritable variation in offspring number, the heritable
variation is autocorrelated across generations. At the individual level
Robertson considered, this is because offspring from large families tend to
beget many descendents themselves (and likewise with small families). The same
autocorrelation occurs at the genomic level, as the perturbations to a neutral
allele's trajectory from its particular fitness background tend to occur in the
same direction across generations as long as the linkage exists and the
selective environment is constant. The additional heritable variation in
offspring number is the additive fitness variation $V_A$, which is inflated by
a factor $Q_t^2$ due to the build up of autocorrelation to generation $t$. We
let $Q^2 := Q_t^2$ as $t \to \infty$. Intuitively, the product $V_A Q^2$
represents the expected total variance in reproductive success a neutral
mutation experiences over its lifetime in a system with weak selection draft.
Incorporating the impact of time-invariant autocorrelation created by draft as
a rescaled rate of drift is analogous to using the Green--Kubo relation to find
the transport coefficient in molecular dynamics with velocity autocorrelation
\parencite{Green1954-kl,Kubo1957-va}.

@@

Equation \eqref{eq:main_Ne} is general, since different modes of selection and
linkage can be accommodated by different expressions for the inflation factor
$Q^2$ \parencite{Santiago1995-hx,Santiago1998-bs}. When fitness variation has a
multiplicative polygenic basis, as it does for genome-wide negative selection
processes, the draft asymptotic effective population size experienced by an
arbitrary neutral site under the influence of all linked regions is,

@@

where the factor of one-half comes from ignoring weak associations from
unlinked regions and chromosomes (see XXX). In our genome-wide model, we
consider the summation in Equation \eqref{eq:polygenic_Ne} over non-overlapping
segments $i \in \{1, 2, \ldots, n\}$ each undergoing selection such that
segment $i$ contributes additive fitness variance $V_{A,i}$ to the total
additive genetic fitness variance. Under equilibrium levels of fitness
variation, the autocorrelation function for a neutral allele associated with
segment $i$ is $C(t) = [(1-r_i)(1-\kappa_i)]^t$, where $r_i$ is the
recombination fraction to the segment and $\kappa_i$ is the rate that the
associated fitness variance decays due to selective dynamics. Then, the
cumulative autocorrelation is,

@@

The remaining pieces are expressions for the equilibrium additive fitness
variance $V_A$ and the decay rate in associated fitness $1-\kappa$. At this
point, we diverge from Santiago and Caballero (\citeyear{Santiago1998-bs},
\citeyear{Santiago2016-mu}) to note that the additive fitness variation is the
sum of additive \emph{genic} fitness variance $V_a$ (i.e. due to allele
frequencies) and the fitness covariance due to linkage disequilibria between
selected sites ($\delta_{LD}$), $V_A = V_a + \delta_{LD}$. Considering only the
genic variation, at equilibrium $\Delta V_{a,i} = 0$; thus, the loss in genic
fitness each generation due to selective dynamics $-\kappa V_{A,i}$ must be
equal to the increase in fitness variation due to new mutations each generation
($V_m$) and changes in the LD term \parencite{Bulmer1971-ae}. Note that the
loss in genic fitness due to drift is not time-invariant due to the build up of
autocorrelation, and considered elsewhere in the derivation (see Supplementary
Materials Equation \ref{eq:vardecay}). Then, at equilibrium $\kappa_i =
\nicefrac{V_{m,i}}{V_{a,i}}$ (see Supplementary Materials Equation \ref{eq:Z}).

@@

When selection is weak, however, the additive fitness variance under the
classic BGS model is no longer accurate. \textcite{Santiago2016-mu} suggested
that this is due to the loss of fitness variation that occurs when a
segregating site fixes and its heterozygosity becomes zero. If we let $R$
represent the rate of the ratchet of deleterious mutations in fixations per
generation, each fixation removes the equivalent amount of equilibrium
variation put in by mutation. Thus, the steady-state genic variance under
mutation and negative selection is (omitting the segment index $i$ for
clarity),

@@

where the condition $V_a \ge 0$ is met when the probability of fixation is less
than or equal to the neutral fixation probability of $\nicefrac{1}{2N}$, which
is held when considering deleterious mutations. This equation connects the
equilibrium additive genic fitness variance to the flux of new variation in due
to new deleterious mutations and the flux out due to their substitution and the
decline in mean population fitness. When $R=0$, the selection is so strong it
cannot fix, and the equilibrium fitness variation is due entirely to young rare
mutations before their extinction $V_a = V_a^{BGS} = Us$. Santiago and
Caballero demonstrate Equation \eqref{eq:Va} through Fisher's Fundamental
Theorem of Natural Selection, but we find an alternative proof
(\cite{Higgs1995-xc}; see Supplementary Materials Section
\ref{supp:weak-strong}). We find that the steady-state additive genic variance
in Equation \eqref{eq:Va} also results from diffusion models with a flux of
mutations into discrete sites (\cite{Kimura1969-jw}).

%Our results differ from \parencite{Santiago2016-mu}, since we find from
%simulations their expression models the additive \emph{genic} fitness
%variation, not additive genetic fitness variation (see Section XXX). This is
%because Equation \eqref{eq:Va} does not capture the expected build-up of
%negative linkage disequilibria when selection is mildly deleterious.

While using Equation \eqref{eq:Va} in Equation \eqref{eq:main_Ne} leads to a
prediction for the draft-effective population size $N_d$, closed-form
expressions for the rate of the ratchet $R$ have generally been hard to find
\parencite{Haigh1978-gt,Higgs1995-xc,Gessler1995-hz}. The key insight of
\textcite{Santiago2016-mu} is that the ratchet rate under draft is determined
by the probability of fixation $p_f(N_d, s)$
\parencite{Kimura1962-su,Malecot1948-zv} with the draft-rescaled effective
population size, i.e. $R = N U p_f(N_d, s)$. Given this equation for the
ratchet and Equation \eqref{eq:polygenic_Ne} for $N_d$ under draft, we have a
system of two non-linear equations that can be solved numerically for $N_d$ and
$R$ for each segment,

@@

Given that Santiago and Caballero's (\citeyear{Santiago2016-mu}) model is a
haploid-model for a single region under equilibrium negative selection, we
first sought to confirm it could accurately predict the reduction in realistic
forward-time simulations of diploid populations with recombination. Using SLiM
\parencite{Haller2019-vu,Haller2023-uk} we simulated a region of $10^5$
basepairs under varying levels of mutation and selection. We find a close
correspondence between the observed and predicted reduction in effective
population size $B=\nicefrac{N_d}{N}$ over all selection and mutation
parameters including weak selection (Figure \ref{fig:figure-1}A), in contrast
to classic BGS theory. Furthermore, to investigate whether this accuracy was
caused by the model accurately predicting the equilibrium fitness variance and
ratchet rate, we also measured these throughout the simulation. Again, we find
the diploid SC16 theory accurately predicts both the ratchet rate (Figure
1\ref{fig:figure-1}B) and the genic fitness variance (Figure
1\ref{fig:figure-1}C).

Additionally, these figures provide further intuition about the underlying
negative selection process. When selection is strong the ratchet rate is zero,
as there is no probability that strongly deleterious can fix. However, around
$2N_e s \approx 1$, the ratchet begins clicking as $p_F > 0$. When this occurs,
fitness variation is reduced from the strong-selection equilibrium by the
amount of population fitness lost per generation due to the ratchet.
Ultimately, the ratchet rate reaches the neutral mutation rate, as $V_a = 0$
and $N_d = N$ (e.g. no draft, pure drift). Likewise, the additive genic fitness
variance matches the level predicted by BGS ($Us$), but begins to diverge when
the ratchet begins clicking. This occurs when the level of variation diverges
from the deterministic mutation-selection equilibrium $V_a = Us$ due to the
stochastic clicking of the ratchet at rate $R$.

@@

Given the accuracy of the SC16 model in predicting the reduction factor $B$ and
ratchet rate for a single segment under general equilibrium mutation negative
selection processes, we extended their model so that it could be applied to
whole-genome data. Our software method \texttt{bgspy} calculates the
equilibrium additive genic fitness variance ($V_a$) and ratchet rate ($R$)
across grids of mutation rates and selection coefficients for each
pre-specified segment in the genome that may be under negative selection (e.g.
coding sequences or UTRs). Then, our method computes a reduction map $B(x)$ for
each position $x$ in the genome by combining the pre-computed $V_a$ for every
segment and a user-supplied recombination map (see Methods XXX). To distinguish
between McVicker's B maps based on classic BGS theory, we call our reduction
map $B(x)$ a B' map.

To assess our predicted B' reduction maps, we simulated negative selection for
fixed mutation rates and selection coefficient on human chromosome 10 using
realistic recombination and conserved feature maps. Averaging over $n=100$
replicates, we estimated the simulation expected reduction map and compared
this to the predicted B and B' maps for the same parameters. We find that our
B' maps and the classic BGS theory B maps closely match simulations when
selection is strong (top row of Figure \ref{fig:figure-1}E). This provides the
first realistic forward-time chromosome-scale simulation confirmation of
classic BGS theory. However, we find slight discrepancies in regions with low
recombination (Figure \ref{fig:figure-1}E). Second, we find our theory is
vastly more accurate than the classic B maps when selection is very weak ($2N_e
s \ll 1$; bottom row of Figure \ref{fig:figure-1}E), which is expected since
BGS theory does not work in this domain. Across all mutation and selection
parameters simulated, the relative error of the classic B maps is 14.6\%
whereas the relative error in the new B' maps is 5\%. Additionally, we find
that the mean squared error between simulations and B' maps is close to the
theoretic lower bound set by the coalescence variance \parencite[see Methods
XXX]{Tajima1983-gu}.

Nearly all of the error between the new B' maps and chromosome-wide simulations
occurs around the drift-barrier domain of $2Ns \approx 1$ (Figure
\ref{fig:figure-1}D). The higher error in this domain occurs across all
mutation rates. We hypothesized that the higher error in this domain may be
because when our method numerically solves Equations \eqref{eq:main_eqns} for
each segment, it does not consider the experienced reduction due to selection
at other linked segments. In particular, we use a fixed drift-effective
$N=1000$ corresponding to the number of diploids in the simulations rather than
$B(x) N$ at position $x$. To test this, we implemented a locally-rescaled
version of the B' maps, which numerically solves Equations \eqref{eq:main_eqns}
for each segment at position $x$ taking into account the reduction experienced
due to selection at other segments by setting $B'(x)N$ as the population size
(see Method XXX). We find the locally-rescaled B' maps reduce the relative
error from 5\% to 0.4\% and mean squared error (Figure \ref{fig:figure-1}D,
dashed colored lines), but does not entirely eliminate the error in the $2Ns
\approx 1$ domain.

@@

Overall, while we find evidence that local-recalling can reduce error rate in
the $2Ns \approx 1$ domain,

it currently cannot be used during when fitting
genome-wide models.

\subsection*{Application to Humans and Model Comparison}

@@

\subsection*{Segment Simulations}

To assess the accuracy of the SC16 theory, we conducted forward simulations
across grids of mutation rates ($\log_{10}(\mu) = \{10^{-9.5}, 10^{-9}, \ldots,
10^{-8}\}$) and selection coefficients ($\log_{10}(\mu) = \{-1, 1.5, 2, \ldots,
4.5\}$) using SLiM \parencite{Haller2023-uk,Haller2019-vu}. Each simulation
evolved a 100kb region with deleterious mutations entering at rate $\mu$
per-basepair, per generation, each with an additive selection coefficient of
$-s$. Total fitness was multiplicative across sites. Each simulation recorded
the number of fixations and the fitness variance per generation. After $10N$
generations, the ARG of the tree was recorded and downstream Python scripts
calculated diversity in the center of the region. We averaged the results of
$10,000$ replicate simulations to compare against theory.

### 2023-06-22 manuscript/supplementary.tex
ms updates

@@

@@

>>>>

\tableofcontents

@@

\section*{Predicted Rate of Fitness Change}

Each fixation of a mutant with fitness effect $-s$ reduces the population
fitness to $1-2s$ since all individuals are homozygotes for the deleterious
mutation and we assume additive effects at a site. For each segment $l$, the
maximum likelihood parameter estimates of our model imply a prediction of the
deleterious substitution rate per segment $\widehat{R}_{l,i}$ for each
selection coefficient $s_i$ in the $m_s$-element DFE grid (according to which
feature class it belongs to).

Since we assume multiplicative fitness effects, the log population fitness
(considering only fixed sites) for segment $l$ in the next generation is,

\begin{align}
    \log(L_{l}) = \sum_{i=1}^{m_s} \log(1-2 s_i) \widehat{R}_{l,i}.
\end{align}
%
Since we assume multiplicative fitness, the total genome-wide log population
fitness in the next generation is

\begin{align}
    \log(L) = \sum_{l} \log{L_l}.
\end{align}
%
This amounts to a predicted population fitness loss per generation of

\begin{align}
    \widehat{\Delta}_W &= 1 - L \\  \nonumber
             &= 1 - \exp\left(\sum_{l} \sum_{i=1}^{m_s} \log(1-2s_i) \widehat{R}_{l,i} \right).
\end{align}
%
We calculate this value for all segments within a feature class, and then sum
over all features to arrive at our genome-wide estimate. We use a parametric
bootstrap to carry forward the estimation uncertainty to the predicted fitness
loss per generation. Briefly, we do this by sampling new estimates of the DFE
per selection coefficient and feature from a normal distribution centered on
the ML point estimate and with the jackknife standard deviation.

@@

\section{Simulations}

\subsection{Segment Simulations}

\section{Additional Theory}

\subsection{supp:weak-strong}
